\documentclass[10pt,a4paper]{moderncv}
\usepackage{datetime}
\moderncvtheme[blue]{casual}      
\nopagenumbers{}       
\usepackage[scale=.75]{geometry}
\geometry{top=1cm, bottom=.5cm}
\recomputelengths                            
\setlength{\parindent}{0pt}
\frenchspacing 
\firstname{Ben}
\familyname{Broadstone}
\title{Software Engineer} 
\phone[mobile]{+1~(202)~733~0824} 
\email{ben.broadstone@protonmail.com}
\social[github]{MR-D05}
\begin{document}
\maketitle
\section{Summary}
Dependable software engineer fluent in PHP, Java, and JavaScriptexemplary interpersonal skills able to conceptualize and deliver. Extensive understanding of end-to-end SDLC best practices. Comfrotable with Laravel, PHP OOP, REST, and MVC design. Strong with Git amd source controle and Docker.
\section{Technical Proficiences}
\cvitem{\textbf{Languages}}{PHP, Java, JavaScript, Typescript, Python}{}{}
\cvitem{\textbf{Frameworks}}{Laravel (7-8) Spring, Angular 9, Symfony, Mulesoft}{}{}
\cvitem{\textbf{Database}}{Illuminate, Oracle, MSSQL, MySQL, PostgreSQL, Hibernate, Doctrine}{}{}
\cvitem{\textbf{Versioning}}{Git, Bitbucket, Jira, Atlassian Suite}{}{}
\cvitem{\textbf{CI/CD}}{Docker, Maven, Bamboo, GitHub Actions}{}{}
\section{Key Achievements}
\begin{itemize}
\item Built unit test suites forl 6 core Laravel repositories.
\end{itemize}
\begin{itemize}
\item{Monitoring, code reviews, deployments, bug fixes, elimination of technical debt. Built jobs for various queues, unit testing.}
\end{itemize}
\begin{itemize}
\item{Symfony tool to provideing real-time data for 150,000 devices.}
\end{itemize}
\section{Experience}
\cventry{January 2021--June 20201}{Software Developer}{Contract}{Bisnow}{}
{\textbf{Key Achievements: Built unit test suites for 6 core Laravel repositories.}
\begin{itemize}
\item {Responsible for website monitoring, code reviews, deployments, interviews, bug fixes, refactoring of critical business logic, and elimination of technical debt. Built out numerous jobs for various repo queues and became proficient at unit testing.}
\end{itemize}}
\cventry{December 2018--Present}{Software Engineer}{Telesystem}{}{}
{\textbf{Key Achievements:}
\begin{itemize}
\item {Implementede an Angular diagnostic tool addressing high impact automatic provisioning issues.}
\end{itemize}
\begin{itemize}
\item {Designed Symphony backend for an active subscriber dashboard.}
\end{itemize}
\begin{itemize}
\item{Write and implement 5+ comprehensive test suites (Acceptance, API, and Unit) for APIs internal to Block Communications.}
\end{itemize}}
\cventry{January 2016--December 2018}{Software Development Intern}{Revature}{}{}{\textbf{Key Achievement:} Built microservice architecture book publishing web application: Spring and Hibernate.}
\cventry{September 2017--January 2018}{Software Development Intern}{Virtual Student Federal Service}{State Department}{}{ \textbf{Key Achievement:} Created staff user management interface using Visual Basic to manage the Residential Security Program of Cappet.}
\section{Hobbies/Projects}
\begin{itemize}
\item{Built a file storage service written in Ada.}
\end{itemize}
\begin{itemize}
\item{ Currently building a BMI tracker in Swift as part of larger fitness app.}
\end{itemize}
\section{Education}
\cventry{January 2016--January 2019}{B.S. Computer Science}{University of Maryland}{}{}{}
\cvitem{\textbf{GPA}}{3.679}
\cvitem{\textbf{Coursework:}}{}
Computer Systems Architecture, Calculus for Engineers I, Calculus for Engineers II, Discrete Math Structures, Data Structures,
Object-Oriented and Concurrent Programming, Advanced Programming Languages, Computer Graphics, Design and Analysis of Computer Algorithms
\end{document}